---
title: "Analysis of Employment and Earnings Based on Different Variables"
subtitle: "Smile and Have Fun!"
author: "Squirrels <br> Caoimhe, Timi, Matthew, Myles and Joseph"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(xaringanExtra)
use_animate_css()
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Get the Data

# Or read in the data manually

employed <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-23/employed.csv')

earn <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-23/earn.csv')


```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```

class: center, middle, animated, rubberBand

## Our goal with this project is investigating the differences in employment and salary and how it is affected by race, sex, age, ethnicity, industry.

---

class: inverse, center, middle, animated, bounceInLeft

# Our Data Set: Employment and Earnings 

---

class: animated, tada

# About our Data Set

- We got our data within the TidyTuesday project found in github.

- The data was collected by the US Bureau of Labour Statistics between the years 2015 and 2020

- We are going to combine two sets of data to create one single data set to answer our question.

- The first data "Earn" contains the variables : sex, race, ethnic origin, age, year, number of persons and median weekly earn.

- The second data set "Employed" contains the variables : industry, major occupation, minor occupation, race, gender, industry total, number employed and year



---

class: middle, center, animated, jello, slower

# First Data set: 
##Earn Data frame 
```{r earnshow, echo = FALSE}
kable(head(earn), format = "html")
``` 


---
class: middle, center, animated, slideInDown, faster
# Second Data set: 
##Employed Data frame 
```{r employedshow, echo = FALSE}
kable(head(employed), format = "html")
``` 

---

class: inverse, center, middle, animated, backInDown
# How we plan to analyse the data 


---
class: animated, flipInY

# What variables we will use 


In this project we will be investigating employment (number of persons) and salary (median weekly earn) and how they are influenced by the variables : 
- Race
- Sex
- Age
- Ethnicity
- Industry
- Year 



---



```{r boring-analysis, echo=FALSE}
n_people = as.numeric(earn$n_persons)
library(ggplot2)
ggplot(earn, aes(x = sex,
                  y = n_people)) +
  geom_boxplot() +
  labs(
    x = "sex",
    y = " Number Employed",
    title = "Number employed based on gender"
    
  )
 
```

---

# What this graph shows
This simple data visualisation shows a small section of the data set comparing the number of men and women employed in the US. As we can see it suggests that there greater number of men employed than women on average.



---
class: inverse, center, middle
#Thank You for watching :)



